Symbolic Weighted Language Models and\\ Quantitative Parsing over Infinite Alphabets

### 2021-07-09 main.tex
petite passe (preuves) 2 premieres section)

%\subsection{Properties}
\noindent
\philippe{Il me manque une explication:  on construit un automate
qui, étant donnée une partition $t$, renvoie la distance minimale
avec n'importe quelle performance (distance donnée par un transducer)?
Quel est le rôle de A(s)?
}
The following property will be useful to the approach on
symbolic weighted parsing presented in Section~\ref{sec:parsing}.

@@

\noindent
Initially, for all $p_1, p_2 \in P$, and $q_1, q_2 \in Q$, let
\[
\wei'_1\bigl( \< p_1, q_1>, \< p_2, q_2>\bigr) =
\wei_1(p_1, p_2) \otimes
\bigl[
\wei_{01}(q_1, q_2)
\oplus
\displaystyle\bigoplus_{\Sigma}
\wei_{11}(q_1, q_2)
\bigr].
\]
\florent{init. $\final'$}

\noindent
Iterate the following for all $p_1\in P$ and $q_1, q_2 \in Q$:
for all $p_2\in P$ and $q_3 \in Q$,
\[
\wei'_1\bigl( \< p_1, q_1>, \< p_2, q_3>\bigr) \opluseq
\displaystyle\bigoplus_{\Sigma} \wei_{10}(q_1, q_2)
\otimes
\wei'_1\bigl( \< p_1, q_2>, \< p_2, q_3>\bigr)
\]
and
\(
\final'(p_1, q_1) \opluseq
\displaystyle\bigoplus_{\Sigma} \wei_{10}(q_1, q_2)
\otimes \final'(p_1, q_2)
\)
\florent{proof correctness (app)}
%\qed
\end{proof}

@@

Algorithm~\ref{algo:Dijkstra}
constructs iteratively two markings
$d_\bot : Q \times Q \to \Semiring$ and
$d_\top : Q \times P \times Q \to \Phic$,
%of the triplets $\<q, \sigma, q'>$
%of states of $A$ by weight values in $\Semiring$,
that converges eventually to $b_\top$ and $b_\bot$.
%It uses for that purpose a priority queue $P$ containing triplets of
%$Q \times \{ \bot, \top \} \times Q$.
%
\noindent
\florent{explication Fig.~\ref{fig:best-update} suivant cas de \eqref{eq:SWVPA-weight}}
The infinite sums in the updates of $d$ in Algorithm~\ref{algo:Dijkstra},
Figure~\ref{fig:best-update}
are well defined
since~$\Semiring$ is complete.

@@

\florent{complete **}
** effectively computable by hypothesis that the label theory is effective**
termination: The algorithm performs $2.|Q|^2$ iterations until $P$ is empty,
and each iteration has a time complexity $O(|Q|^2 . |P|)$.
\florent{detail with nb tr. and states}
That gives a time complexity $O(|Q|^4 . |P|)$.
It can be reduced by implementing $P$ as a priority queue,
prioritized by the value returned by $d$.
%$|Q|^3.\log(|Q|^2)$
%
At termination, $d_\bot = b_\bot$ and $d_\top = b_\top$
(see Appendix~\ref{sec:bestsearch}).
With~\eqref{eq:min}, this ensures
the correctness of Algorithm~\ref{algo:Dijkstra}.

\noindent
In order to obtain effectively a witness
(word of $\Delta^*$ with a computation of $A$ of minimal weight),
we require the additional property of convexity of weight functions.***
\florent{completer}

>>>>

%\subsection{Properties}
\noindent
\philippe{Il me manque une explication:  on construit un automate
qui, étant donnée une partition $t$, renvoie la distance minimale
avec n'importe quelle performance (distance donnée par un transducer)?
Quel est le rôle de A(s)?
}
\florent{ajout d'une explication avant le Corrolaire}
The following property will be useful to the approach on
symbolic weighted parsing presented in Section~\ref{sec:parsing}.

@@

\noindent
Initially, for all $p_1, p_2 \in P$, and $q_1, q_2 \in Q$, let
\[
\begin{array}{rcl}
\wei'_1\bigl( \< p_1, q_1>, \< p_2, q_2>\bigr) & = & 
\wei_1(p_1, p_2) \otimes
\bigl[
\wei_{01}(q_1, q_2)
\oplus
\displaystyle\bigoplus_{\Sigma}
\wei_{11}(q_1, q_2)
\bigr]\\
\final'(p_1, q_1) & = & \final_A(p_1) \otimes \final_T(q_1)
\end{array}
\]

\noindent
Then, we iterate the following for all $p_1\in P$ and $q_1, q_2 \in Q$:
for all $p_2\in P$ and $q_3 \in Q$,
\[
\begin{array}{rcl}
\wei'_1\bigl( \< p_1, q_1>, \< p_2, q_3>\bigr) & \opluseq & 
\displaystyle\bigoplus_{\Sigma} \wei_{10}(q_1, q_2)
\otimes
\wei'_1\bigl( \< p_1, q_2>, \< p_2, q_3>\bigr)\\
\final'(p_1, q_1) & \opluseq & 
\displaystyle\bigoplus_{\Sigma} \wei_{10}(q_1, q_2)
\otimes \final'(p_1, q_2)
\end{array}
\]
\florent{proof correctness (app)}
%\qed
\end{proof}

@@

Algorithm~\ref{algo:Dijkstra}
constructs iteratively two markings
$d_\bot : Q \times Q \to \Semiring$ and
$d_\top : Q \times P \times Q \to \Phic$,
%of the triplets $\<q, \sigma, q'>$
%of states of $A$ by weight values in $\Semiring$,
that converges eventually to $b_\top$ and $b_\bot$.
%It uses for that purpose a priority queue $P$ containing triplets of
%$Q \times \{ \bot, \top \} \times Q$.
%
\noindent
\florent{explication Fig.~\ref{fig:best-update} (update) suivant cas de \eqref{eq:SWVPA-weight}?}
The infinite sums in the updates of $d$ in Algorithm~\ref{algo:Dijkstra},
Figure~\ref{fig:best-update}
are well defined
since~$\Semiring$ is complete.

@@

Termination: the algorithm performs $2.|Q|^2$ iterations until $P$ is empty,
and each iteration has a time complexity $O(|Q|^2 . |P|)$.
\florent{complexity: detail with nb tr. and states?}
That gives a time complexity $O(|Q|^4 . |P|)$.
It can be reduced by implementing $P$ as a priority queue,
prioritized by the value returned by $d$.
%$|Q|^3.\log(|Q|^2)$
%
At termination, $d_\bot = b_\bot$ and $d_\top = b_\top$
(see Appendix~\ref{sec:bestsearch}).
With~\eqref{eq:min}, this ensures
the correctness of Algorithm~\ref{algo:Dijkstra}.

\noindent
** effectively computable by hypothesis that the label theory is effective**
\florent{REVOIR}
In order to obtain effectively a witness
(word of $\Delta^*$ with a computation of $A$ of minimal weight),
we require the additional property of convexity of weight functions.***
